Simulating spaces and stressors

### 2024-03-19 Analysis/01_Simulating_spaces_and_stressors.Rmd
removed legend

## Stressors
plot.text.box("1) Resampling\nwith stressor:\nnull mechanism", cex = 2)
plot.1D(trait_space, reduction = random_reduction, null = rep(TRUE, 200), main = "1D null mechanism", legend = c("Full distribution (200sp)", "Resample (100sp)"))
plot.2D(trait_space, reduction = random_reduction, null = !random_reduction, main = "2D null mechanism")

plot.text.box("2) Resampling\nwith stressor:\nfiltering\nmechanism", cex = 2)
plot.1D(trait_space, reduction = filtering_reduction, null = random_reduction, main = "1D filtering mechanism", legend = c("Random resampling (100sp)", "Biased resampling (100sp)"))
plot.2D(trait_space, reduction = filtering_reduction, null = random_reduction, main = "2D filtering mechanism")

>>>>

## Stressors
plot.text.box("1) Resampling\nwith stressor:\nnull mechanism", cex = 2)
plot.1D(trait_space, reduction = random_reduction, null = !random_reduction, main = "1D null mechanism")
plot.2D(trait_space, reduction = random_reduction, null = !random_reduction, main = "2D null mechanism")

plot.text.box("2) Resampling\nwith stressor:\nfiltering\nmechanism", cex = 2)
plot.1D(trait_space, reduction = filtering_reduction, null = random_reduction, main = "1D filtering mechanism")
plot.2D(trait_space, reduction = filtering_reduction, null = random_reduction, main = "2D filtering mechanism")
